Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-25 main.tex
add defs
Plus de formalisme
ENTCS style + package
proof
update defs
authors
new restriction: boolean networks
defs + proof
more defs
intro
title, keywords & abstract

\documentclass{article}

%\usepackage{hyperref}

@@

\usepackage{url}     % Mise en forme + liens pour URLs
\usepackage{array}   % Tableaux évolués

@@

\usepackage{prettyref}
\newrefformat{def}{Def.~\ref{#1}}
\newrefformat{fig}{Fig.~\ref{#1}}
\newrefformat{pro}{Property~\ref{#1}}
\newrefformat{pps}{Proposition~\ref{#1}}
\newrefformat{lem}{Lemma~\ref{#1}}
\newrefformat{thm}{Theorem~\ref{#1}}
\newrefformat{sec}{Sect.~\ref{#1}}
\newrefformat{ssec}{Subsect.~\ref{#1}}
\newrefformat{suppl}{Appendix~\ref{#1}}
\newrefformat{eq}{Eq.~\eqref{#1}}
\def\pref{\prettyref}

\usepackage{ntheorem}
\theorembodyfont{\upshape}
\newtheorem{definition}{Definition}{}{}
\newtheorem*{example}{Example}{}{}
%\newtheorem{property}{Property}{}{}
%\newtheorem{proposition}{Proposition}{}{}

@@

\input{macros/macros}
\input{macros/macros-ph}
%\input{macros/macros-grn}

% Macros
\newcommand{\sN}{\mathbb{N}}
\def\DEF{\stackrel{\Delta}=}
\def\EQDEF{\stackrel{\Delta}\Leftrightarrow}
\newcommand{\segm}[2]{\llbracket #1; #2 \rrbracket}
\def\indexes#1{\mathbb{I}^{#1}}
\newcommand{\sfp}[3]{\mathbf{sfp}\{#1\}\left(#2\mapsto#3\right)}
%\def\lfp{\f{pppf}\;}

% Commandes À FAIRE
\usepackage{color} % Couleurs du texte
\newcommand{\towrite}[1]{\textcolor{blue}{#1}}
\newcommand{\todo}[1]{\textcolor{red}{[#1]}}

@@

\title{\todo{Le titre}}

\author{\todo{Les auteurs}}

\begin{document}

\maketitle

\begin{abstract}
\todo{L'abstract}
\end{abstract}

\section{Introduction}\label{sec:intro}
\towrite{Intro}

\section{The PH Framework}\label{sec:def-ph}
\todo{Définir les priorités fixes}
\input{parts/def-ph}

\section{Static analysis}\label{sec:sa}
\towrite{Reprendre définitions de l'analyse statique}
\todo{Ajouts pour les priorités fixes}
\input{parts/sa}

@@

\bibliographystyle{plain}
\bibliography{biblio}

>>>>

\documentclass{entcs}

\usepackage{entcsmacro}

@@

\usepackage{url}     % Mise en forme + liens pour URLs
\usepackage{hyperref}
\usepackage{array}   % Tableaux évolués

@@

\usepackage{prettyref}
\newrefformat{def}{Def.~\ref{#1}}
\newrefformat{fig}{Fig.~\ref{#1}}
%\newrefformat{prop}{Property~\ref{#1}}
\newrefformat{prop}{Proposition~\ref{#1}}
\newrefformat{lem}{Lemma~\ref{#1}}
\newrefformat{th}{Theorem~\ref{#1}}
\newrefformat{co}{Corollary~\ref{#1}}
\newrefformat{sec}{Sect.~\ref{#1}}
\newrefformat{ssec}{Subsect.~\ref{#1}}
\newrefformat{suppl}{Appendix~\ref{#1}}
\newrefformat{eq}{Eq.~\eqref{#1}}
\def\pref{\prettyref}

%\usepackage{ntheorem}
%\theorembodyfont{\upshape}
%\newtheorem{definition}{Definition}{}{}
%\newtheorem*{example}{Example}{}{}
%\newtheorem{property}{Property}{}{}
%\newtheorem{proposition}{Proposition}{}{}

@@

\input{macros/macros}
\input{macros/macros-ph}
\input{macros/macros-abstr}

% Macros
\newcommand{\sN}{\mathbb{N}}
\def\DEF{\stackrel{\Delta}=}
\def\EQDEF{\stackrel{\Delta}\Leftrightarrow}
\newcommand{\segm}[2]{\llbracket #1; #2 \rrbracket}
\def\indexes#1{\mathbb{I}^{#1}}
\newcommand{\sfp}[3]{\mathbf{lfp}\{#1\}\left(#2\mapsto#3\right)}
%\def\lfp{\f{pppf}\;}
\def\f#1{\mathsf{#1}}
\def\prio{\mathsf{prio}}
\newcommand{\bottom}{\perp}
\newcommand{\Vs}{V_\PHs}
\newcommand{\Vh}{V_\PHh}
\newcommand{\Va}{\Vh}
\newcommand{\stable}{\mathsf{stable}}
\newcommand{\update}{\mathsf{update}}
\newcommand{\components}{\Gamma}
\newcommand{\cs}{CS}

\tikzstyle{prio}=[draw,double,-stealth]

\def\restriction#1#2{\mathchoice
              {\setbox1\hbox{${\displaystyle #1}_{\scriptstyle #2}$}
              \restrictionaux{#1}{#2}}
              {\setbox1\hbox{${\textstyle #1}_{\scriptstyle #2}$}
              \restrictionaux{#1}{#2}}
              {\setbox1\hbox{${\scriptstyle #1}_{\scriptscriptstyle #2}$}
              \restrictionaux{#1}{#2}}
              {\setbox1\hbox{${\scriptscriptstyle #1}_{\scriptscriptstyle #2}$}
              \restrictionaux{#1}{#2}}}
\def\restrictionaux#1#2{{#1\,\smash{\vrule height .8\ht1 depth .85\dp1}}_{\,#2}}

% Commandes À FAIRE
\usepackage{color} % Couleurs du texte
\definecolor{darkgreen}{rgb}{0,0.5,0}
\newcommand{\towrite}[1]{\textcolor{darkgreen}{[#1]}}
\newcommand{\todo}[1]{\textcolor{red}{[[#1]]}}

@@

\def\lastname{Folschette \emph{et al}}

\begin{document}
\begin{frontmatter}
\title{Under-approximation of reachability through static analysis in multivalued asynchronous networks}

\author{Maxime Folschette\thanksref{myemail}}
\address{\towrite{PRES LUNAM + IRCCyN}}
\thanks[myemail]{\url{Maxime.Folschette@irccyn.ec-nantes.fr}}

\author{Loïc Paulevé}
\address{\towrite{ETZH}}

\author{Morgan Magnin\thanksref{myemail}}
\address{\towrite{PRES LUNAM + IRCCyN}}

\author{Olivier Roux\thanksref{myemail}}
\address{\towrite{PRES LUNAM + IRCCyN}}

\begin{abstract}

The Process Hitting is a recent framework based on the play of concurrent actions.
Each action can modify the state of a component, and is conditioned by the state of at most one other component.
Its original definition does not involve priorities between actions, allowing very efficient static analysis based on local causality to compute reachability properties.
Although a new definition of the framework has been proposed including classes of priorities for actions,
the static analysis methods were not adapted and thus did not apply to this extension of the framework.

In this paper, we focus on a restriction of the Process Hitting with priorities by considering a class of models equivalent to multivalued networks.
Then, we develop a new refinement for the under-approximation of the static analysis to give accurate results for this set of Process Hitting models.

\end{abstract}
\begin{keyword}
qualitative modelling,
model abstraction,
static analysis,
asynchronous network
\end{keyword}
\end{frontmatter}

\input{parts/intro}

\input{parts/def-ph}

\input{parts/sa}

@@

\bibliographystyle{entcs}
\bibliography{biblio}
